\documentclass[letterpaper,12pt]{article} % Set base font size to 12pt

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Set body font size to 14pt
\fontsize{14pt}{16pt}\selectfont

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\Large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Vincent Feng} \\ \vspace{1pt}
    \small 647-819-2666 $|$ \href{mailto:x@x.com}{\underline{vince4ho@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/vincent-feng-66155a27a/}{\underline{linkedin.com/in/vf123098}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Western University}{London, ON}
      {HSp Bachelor's of Computer Science}{September 2022 -- August 2026}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Customer Service Representative}{July 2025 -- September 2025}
      {Wine Butler}{}
      \resumeItemListStart
        \resumeItem{Showed customers how to use Wine Butler's bottling services and established a comfortable and helpful environment for customers.}
        \resumeItem{Aided those unable to bottle in the process.}
        \resumeItem{Processed and input customer orders into internal system, ensuring 100\% accuracy and reducing order errors}
        \resumeItem{Collected payment from customers in person or online.}
      \resumeItemListEnd

    \resumeSubheading
      {Information Technology Support Specialist}{May 2023 -- September 2023}
      {Times Optical Inc}{}
      \resumeItemListStart
        \resumeItem{Configured and deployed Windows-based desktops and laptops for internal staff, including OS installations and driver updates.}
        \resumeItem{Diagnosed and resolved hardware and software issues, ensuring minimal downtime.}
        \resumeItem{Assisted in basic network setup and connectivity troubleshooting.}
    \resumeItemListEnd

    \resumeSubheading
      {Web Developer}{July 2024 -- April 2025}
      {Lens4you}{}
      \resumeItemListStart
        \resumeItem{Designed, developed, and deployed an e-commerce website using WordPress, HTML/CSS, and PHP.}
        \resumeItem{Integrated third-party plugins and custom features to support online sales and customer engagement.}
        \resumeItem{Performed ongoing site maintenance, updates, and optimization to ensure consistent uptime and performance.}
        \resumeItem{Consistently implementing UX improvements based on feedback.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Technical Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{MyWishlist} $|$ \emph{Python, React, PostgreSQL, Node.js}}{December 2024 -- Present}
          \resumeItemListStart
            \resumeItem{Developed a full-stack wishlist tracking web app using the MERN-like stack (React frontend, Node.js backend).}
            \resumeItem{Integrated PostgreSQL to store and retrieve user data; optimized database queries for performance.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, C/C++, SQL (Postgres), JavaScript, HTML/CSS} \\
     \textbf{Frameworks}{: React, Node.js, JUnit, WordPress, Material-UI} \\
     \textbf{Developer Tools}{: Git, Google Cloud Platform, VS Code, Visual Studio, PyCharm, IntelliJ, Eclipse} \\
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
